\subsection{Time evolution of $G_{\rm eff}(t)$ and BBN consistency}

\subsubsection{Phasing of condensation and confinement}

The formation of a neutrino condensate and subsequent cosmological confinement
do not occur instantaneously. We identify three epochs:

\paragraph{Epoch I: Pre-condensation ($t < 1$ s, $T > 1$ MeV).}
The neutrinos are in thermal equilibrium with weak interaction. Pairing
starts at $T \sim 100$ GeV, but full condensation requires decoupling
from a thermal bath.

\paragraph{Epoch II: BBN ($t \sim 1-200$ s, $T \sim 0.1-1$ MeV).}
The condensate is "young" - pairs exist, but cosmological confinement
is not yet fully active. Binding energy:
\begin{equation}
E_{\rm pair}^{\rm BBN} \approx E_0 + \epsilon_{\rm early}
\end{equation}
where $\epsilon_{\rm early} \ll \kappa_{\rm conf} \ln(1+z_{\rm BBN})$
is a small increment.

\paragraph{Epoch III: Post-BBN ($t > 200$ s).}
Full cosmological confinement begins. Binding energy:
\begin{equation}
E_{\rm pair}(z) = E_0 + \kappa_{\rm conf} \ln(1+z) \times f(t - t_{\rm BBN})
\end{equation}
where $f$ is a smooth "turn-on" function ($f \approx 0$ for $t \sim t_{\rm BBN}$,
$f \to 1$ for $t \gg t_{\rm BBN}$).

\subsubsection{BBN consistency check}

During BBN epochs ($z \sim 10^9$):
\begin{equation}
\frac{G(t_{\rm BBN})}{G_0} \approx 1 + \delta G_{\rm BBN}
\end{equation}

where $\delta G_{\rm BBN}$ is a small correction from the early-stage condensate.

For $B(\Psi) \sim E_{\rm pair}^\alpha$ with $\alpha \sim 1$:
\begin{equation}
\left|\frac{\Delta G}{G}\right|_{\rm BBN}
= \left|\frac{G(t_{\rm BBN}) - G(t_0)}{G(t_0)}\right|
\lesssim \alpha \frac{\epsilon_{\rm early}}{E_0} \ll 0.2
\end{equation}

For $\epsilon_{\rm early}/E_0 \sim 0.1$ (order estimate):
\begin{equation}
\left|\frac{\Delta G}{G}\right|_{\rm BBN} \sim 0.1 \quad \checkmark
\end{equation}

\textbf{Conclusion:} Delayed onset of full confinement ensures
consistency with BBN limits.

\subsubsection{Testable prediction}

From BBN to today:
\begin{equation}
\frac{G(t_0)}{G(t_{\rm BBN})} \approx 0.9 \pm 0.1
\end{equation}

→ Measurable by future accurate BBN simulations or lunar laser ranging